MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Model Selection

### 2020-04-20 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
scale continuous vars

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "PMI", 
                                                             "ageOfDeath", "RIN", "RIN2", "EV.1", 
                                                             "EV.2", "EV.3", "EV.4", "EV.5")))
phase1
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`

>>>>

# Stepwise regression
phase1 <- mvBIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula, 
                         data = COVARIATES,
                         variables = array(c("(1|Institution)", "(1|Reported_Gender)", "scale(PMI)", 
                                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)", 
                                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
phase1
```
Clinical and technical variables selected in phase I are `r paste(adjust.covars, collapse = ', ')`
